Figures

### 2019-07-29 figures/02_hierarchical_demo.Rmd
cartography and panel arragement

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
cl            <- cart_layers()
ep            <- cl$ep
states        <- cl$states
study_bbox    <- cl$study_bbox

dt            <- readRDS("../data/dt.rds")

ids <- dt %>%
  group_by(hu4_zoneid) %>% 
  tally()

hu4 <-  LAGOSNEgis::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
  st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))

n_cat  <- 6
colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
hu4    <- mutate(hu4, 
            n_cat = cut(hu4$n, breaks = 
                          classInt::classIntervals(hu4$n, n = n_cat)$brks))
hu4 <- dplyr::filter(hu4, !is.na(n_cat))

@@

gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, aes(fill = n_cat), color = "black", size = 0.4) +
  scale_fill_manual(values = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15")) +
    coord_sf(datum = NA) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
  ggtitle("# of lakes per region")

cowplot::plot_grid(
  plot_grid(nullGrob(), gg_lines, nullGrob(), 
            ncol = 1, rel_heights = c(0.52, 1, 0.51)), 
  gg_hu4, rel_widths = c(0.7, 1))
```

>>>>

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
# cl            <- cart_layers()
# ep            <- cl$ep
# states        <- cl$states
# study_bbox    <- cl$study_bbox

study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
ep            <- st_read("../data/gis.gpkg", "ep", quiet = TRUE)
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4           <- st_read("../data/gis.gpkg", "hu4s", quiet = TRUE)

dt            <- readRDS("../data/dt.rds")
ids           <- dt %>%
  group_by(hu4_zoneid) %>% 
  tally()

hu4    <-  hu4 %>%
  # st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))
n_cat  <- 6
colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
hu4    <- mutate(hu4, 
            n_cat = cut(hu4$n, breaks = 
                          classInt::classIntervals(hu4$n, n = n_cat)$brks))
hu4    <- dplyr::filter(hu4, !is.na(n_cat))

@@

gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, aes(fill = n_cat), color = "black", size = 0.4) +
  scale_fill_manual(values = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15")) +
    coord_sf(datum = NA) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
  ggtitle("# of lakes per region")

cowplot::plot_grid(gg_hu4,
  plot_grid(nullGrob(), gg_lines, nullGrob(), 
            ncol = 1, rel_heights = c(0.52, 1, 0.51)), 
  rel_widths = c(1, 0.7))
```

### 2019-07-29 figures/07_model-selection.Rmd
cartography and panel arragement

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
cl            <- cart_layers()
states        <- cl$states
study_bbox    <- cl$study_bbox

# map significant random effects hu4s
gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    coord_sf(datum = NA) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

>>>>

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)

# map significant random effects hu4s
gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    coord_sf(datum = NA) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))  +
  ggtitle("Ag sensitive regions")
